Learning a functional distance between organizations with unsupervised embeddings of scientific mobility

### 2020-08-03 paper/current/main.tex
edits s2 fig

%
% Figure - descriptives
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Descriptive/mobility_by_country.pdf}
	\caption{
		\textbf{Extent and nature of mobility by country.}
		\textbf{a.}
		The proportion of researchers in each country classified as mobile, meaning that they have at least two organization affiliations within the period of study.
		The countries with the most mobile researchers are the United States, China, France, Great Britain, and Germany.
		\textbf{b.}
		The same information, arranged into a cumulative distribution.
		The five countries with the highest mobility account for approximately 70 \% of all mobility.
		\textbf{c.} The proportion of researchers labeled as mobile by country.
		\textbf{d.} First two principal components of four variables: proportion in each country mobile across organizations, proportion mobile across cities, proportion mobile across regions, and proportion mobile across countries.
		The first component captures the overall degree of mobile, whereas the second compares within-country against across-country mobility.
	}
	\label{fig:supp:descriptives}
\end{figure}

>>>>

%
% Figure - descriptives
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Descriptive/mobility_by_country.pdf}
	\caption{
		\textbf{Extent and nature of mobility by country.}
		\textbf{a.}
		The proportion of all mobile researchers contributed by each country. 
		Over 30\% of all mobile researchers have been affiliated with organizations in the U.S. during the period of study.
		\textbf{b.}
		Cumulative distribution of data shown in (\textbf{a}).
		The U.S., China, and France, the U.K., and Germany comprise about 70\% of all mobile researchers. 
		\textbf{c.} 
		The proportion of each country's researchers who are mobile.
		The dashed line indicates the proportion of all researchers in the data who are mobile. 
		France, followed by Qatar and the U.S. have the highest proportion of mobile researchers. 
		\textbf{d.} First two principal components of four variables: proportion of researchers in each country mobile across organizations, proportion mobile across cities, proportion mobile across regions, and proportion mobile across countries.
		The countries are roughly sorted in order of the number of mobile researchers and the fraction of international mobile researchers in the first and second principal components, which are indicated by PC1 and PC2, respectively. 
		PC1 explains 88.3\% of the total variance, whereas PC2 explains 9.5\% of the total variance. 
	}
	\label{fig:supp:descriptives}
\end{figure}
